### 2015-05-18 inst/examples/ipm_sims_example.Rmd
adds new function to calculate synchrony metrics from ipm output; fixes #4

---
output: html_document
---
# Checking IPM simulation output
```{r read_data}
library(plyr)
library(reshape2)
library(ggplot2)
output_list <- readRDS("../../results/ipm_simulation_lists.RDS")
mlist <- melt(output_list)
```

@@

## Run through synchrony library
```{r get_synchs}
# library(communitySynchrony)
# get_comm_synchrony(ts_data = subset(mlist, L2=="ENVDEMO" & L1=="Arizona"))
```

>>>>

---
output: html_document
---
# Checking IPM simulation output
```{r read_data}
library(plyr)
library(reshape2)
library(ggplot2)
library(synchrony)
output_list <- readRDS("../../results/ipm_simulation_lists.RDS")
mlist <- melt(output_list)
```

@@

## Run through synchrony library
```{r get_synchs}
library(communitySynchrony)
colnames(mlist)[1:3] <- c("year", "species", "cover")
ts_data <- subset(mlist, L2=="ENVDEMO" & L1=="Arizona")[1:3]
test1 <- get_ipm_synchrony(ts_data = ts_data)
str(test1)
```
